Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2019-01-15 paper/paper.tex
Fix minor err

%%%%%%%%%%%%%%%%%%%%
%Main
%%%%%%%%%%%%%%%%%%%%
\begin{document}
\clearpage{}
\begin{abstract}
  {\normalsize Atomically thin porous graphene membranes areis
    emerging as one of the most promising candidates for the
    next-generation membrane technologymaterial owing to the ultrahigh
    permeation. However, the transport selectivity relies on the
    precise control over pore size and shape, which considerably
    limitingcompromises the scalability. Here, we study electrolyte
    permeation through a sheet of large-area, porous graphene
    membrane, with relatively large pore sizes of 20$\pm$10
    nanometers. Counterintuitively, we observe macroscopica high
    degree of salt rejection is observed by applying
    electrostaticallyelectrostatic gating, which reducesreducing the
    diffusive flux by up to one order of magnitude. We systematically
    investigate the effects of salt concentration and species,
    including developing a theory to model the electrolyte diffusion
    through a nanopore drilled in a sheet of gated graphene. The
    interplay between graphene quantum capacitance and the electrical
    double layer is found to selectively modulate the anionic and
    cationic transport paths, creating voltage-dependent
    electrochemical barriers when the pore size is comparable to the
    Debye length. Our findings reveal a new degree of freedom
    regulating electrolyte permeation through porous two-dimensional
    materials.
    % Atomically thin porous graphene is emerging as one of
    % the most promising candidates for the next-generation membrane
    % technology owing to the ultrahigh permeation. However, the
    % transport selectivity relies on the precise control over pore size
    % and shape, considerably limiting the scalability. Here, we study
    % electrolyte permeation through a sheet of large-area, porous
    % graphene membrane, with relatively large pore sizes of 20$\pm$10
    % nanometers. Counterintuitively, we observe macroscopic salt
    % rejection by applying electrostatically gating, which reduces the
    % diffusive flux by up to one order of magnitude. We systematically
    % investigate the effects of salt concentration and species,
    % including developing a theory to model the electrolyte diffusion
    % through a nanopore in a sheet of gated graphene. The interplay
    % between graphene quantum capacitance and the electrical double
    % layer is found to selectively modulate the anionic and cationic
    % transport paths, creating voltage-dependent electrochemical
    % barriers when the pore size is comparable to the Debye length. Our
    % findings reveal a new degree of freedom regulating electrolyte
    % permeation through porous two-dimensional materials.   
    % Atomically thin porous graphene membranes are emerging
    % as one of the most promising candidates as next-generation
    % membrane technology owing to their unique transport physics and
    % high permeation. Among the current challenges of 2D membranes is
    % the understanding of fundamental ion transport as well as its
    % control towards applications in ion rectification, ionic
    % transistors or desalination.  Here we report the study of
    % tailoring the ion transport through atomically-thin porous
    % graphene with pore sizes of 20$\pm$10 nanometers, and a pore
    % density of 1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$. By
    % electrostatically gating a sheet of porous graphene, we
    % demonstrate a considerable reduction of salt flux by up to 55\%
    % and 85\% using a gate voltage, based on our experiments and
    % theoretical predictions, respectively. We systematically
    % investigate the effects of salt concentration and species,
    % including the development of a theory to model the electrolyte
    % diffusion through a nanopore in a sheet of gated graphene. The
    % interplay between graphene quantum capacitance and electrical
    % double layer is identified to be the main mechanism responsible
    % for the observed salt flux reduction, when the pore size is
    % comparable to the Debye length. Our findings reveal a new degree
    % of freedom controlling the membrane potential and electrolyte
    % permeation through porous two-dimensional materials.
  }
\end{abstract}

@@

In summary, we have presented a comparative experimental and modelling
study on macroscopic salt rejection through a sheet of large-area
porous graphene under electrostatic gating. We show that due to a
small quantum capacitance of atomically-thin graphene, the graphene
surface potential is considerably lower than the applied gate
voltage. As a result, the subtle redistribution of the electrochemical
potentials create new pathways for ionic transport, which in turn lead
to a considerable degree of salt rejection. We report a high degree of
salt rejection at $V_{\mathrm{G}}$ = 1.25 V by approximately one order
of magnitude, based on our experiments and theoretical predictions,
respectively. We demonstrate that the observed salt rejection
positively correlates with the Debye length that nonlinearly modulates
the graphene surface potential and charge density. The experimental
results and fundamental principles presented here open an avenue
towards realization of atomically thin 2D porous membranes for
advanced separation process in electrolyte solutions.

>>>>

%%%%%%%%%%%%%%%%%%%%
%Main
%%%%%%%%%%%%%%%%%%%%
\begin{document}
\clearpage{}
\begin{abstract}
  {\normalsize Atomically thin porous graphene is emerging as one of
    the most promising candidates for next-generation membrane
    material owing to the ultrahigh permeation. However, the transport
    selectivity relies on the precise control over pore size and shape
    which considerably compromises the scalability. Here, we study
    electrolyte permeation through a sheet of large-area, porous
    graphene, with relatively large pore sizes of 20$\pm$10
    nanometers. Counterintuitively, a high degree of salt rejection is
    observed by electrostatic gating, reducing the diffusive flux by
    up to one order of magnitude. We systematically investigate the
    effects of salt concentration and species, including developing a
    theory to model the electrolyte diffusion through a nanopore
    drilled in a sheet of gated graphene. The interplay between
    graphene quantum capacitance and the electrical double layer is
    found to selectively modulate the anionic and cationic transport
    paths, creating voltage-dependent electrochemical barriers when
    the pore size is comparable to the Debye length. Our findings
    reveal a new degree of freedom regulating electrolyte permeation
    through porous two-dimensional materials.  }
\end{abstract}

@@

In summary, we have presented a comparative experimental and modelling
study on macroscopic salt rejection through a sheet of large-area
porous graphene under electrostatic gating. We show that due to a
small quantum capacitance of atomically-thin graphene, the graphene
surface potential is considerably lower than the applied gate
voltage. As a result, the subtle redistribution of the electrochemical
potential creates new pathways for ionic transport, which in turn
leads to a considerable degree of salt rejection. We report a high
degree of salt rejection at $V_{\mathrm{G}}$ = 1.25 V by approximately
one order of magnitude, based on our experiments and theoretical
predictions, respectively. We demonstrate that the observed salt
rejection positively correlates with the Debye length that nonlinearly
modulates the graphene surface potential and charge density. The
experimental results and fundamental principles presented here open an
avenue towards realization of atomically thin 2D porous membranes for
advanced separation process in electrolyte solutions.
